Last glacial cycle glacier erosion potential in the Alps

### 2021-02-04 articles/erosion/alps-erosion.tex
Add discussion of sediments preventing erosion.

    \ian{It might be worth mentioning/discussing the role of ``till dilatation''
      in the sliding relationship. There are a lot of interpretations, but
      the erosion rule is thought to be a proxy for glacier abrasion of a glacier flowing
      over a hard bed. Thus if there is a layer of till present it is arguable
      if such abrasion can occur. Given the uncertainties, I doubt this factor
      changes the story very much. However, it might be worth mentioning
      something (somewhere) about how multiple processes are lumped together in
      the sliding relationship or that till processes are uncertain due to the
      unknown distribution of till. This could ease some reviewer concerns.  }

@@

    That said, the magnitude of the modelled erosion rates can hardly be used
    as a criteria to rule out this or that erosion law for the glacial Alps, as
    all these laws are affected with very large uncertainties. Thus it can not
    be excluded that a linear or sub-linear erosion-law
    \citep[e.g.,][]{Cook.etal.2020} would lead to a less localized pattern of
    erosion (Fig.~\ref{fig:powerlaws}c and~d), and a stronger correlation
    between modelled ice volume and erosion (Fig.~\ref{fig:powerlaws}k and~l).
    Even then, the intrinsically large variations in modelled glacier sliding
    velocities yield cumulative glacial-cycle erosion two to three orders of
    magnitude higher in the Alpine valley than near the mountain tops
    (Fig.~\ref{fig:powerlaws}d).

    \todo{Insert discussion of sediments here.}

>>>>

@@

    That said, the magnitude of the modelled erosion rates can hardly be used
    as a criteria to rule out this or that erosion law for the glacial Alps.
    Firstly, while sliding is here modelled by a pseudo-plastic law based on
    till dilatation under high water pressure \citep{Tulaczyk.etal.2000},
    empirical erosion rules are thought to be a proxy for glacier abrasion
    \note{and plucking?} of a glacier flowing over a hard bed. Secondly, it is
    arguable that a layer of till and proglacial sediments may have hindered
    erosion for at least parts of the glacial cycle. Finally, all empirical
    erosion laws are affected with very large uncertainties. Thus it can not
    be excluded that a linear or sub-linear erosion-law
    \citep[e.g.,][]{Cook.etal.2020} would lead to a less localized pattern of
    erosion (Fig.~\ref{fig:powerlaws}c and~d), and a stronger correlation
    between modelled ice volume and erosion (Fig.~\ref{fig:powerlaws}k and~l).
    Even then, the intrinsically large variations in modelled glacier sliding
    velocities yield cumulative glacial-cycle erosion two to three orders of
    magnitude higher in the Alpine valley than near the mountain tops
    (Fig.~\ref{fig:powerlaws}d).
